On g~0~

### 2017-03-15 manuscript.Rmd
kerstiens has species; load TRY category dataset

Barnard and Bauerle said so too but gave no details.
Even in very good datasets, g0 and g1 are strongly correlated (Figure 2).
Across datasets, g0 increases when the model fits poorly (Figure 3), and the width of the confidence interval increases when less variation in a ball-berry coefficient.
Often g0 is even negative [@heroult2013; @leuning1990], so it is often set to some arbitrary value

@@

@@

@santrucek Direct measurements showing much higher 'cuticular' conductance of the leaf side with stomata, though stomata were closed. In agreement with @kerstiens1996 who showed 10x higher gmin for stomatal side vs. non-stomatal cuticle.

>>>>

Barnard and Bauerle said so too but gave no details.
Even in very good datasets, g0 and g1 are strongly correlated (Figure 2).
Across datasets, g0 increases when the model fits poorly (Figure 3), and the width of the confidence interval increases when less variation in a ball-berry coefficient.
Often g0 is even negative [@heroult2013; @leuning_modelling_1990], so it is often set to some arbitrary value

@@

Hygen 1951 early work showing MLD method

@@

santrucek Direct measurements showing much higher 'cuticular' conductance of the leaf side with stomata, though stomata were closed. In agreement with @kerstiens1996 who showed 10x higher gmin for stomatal side vs. non-stomatal cuticle.
